Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
Mer svar til Martin om one-size-fits-all
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@79 43ef1190-90fd-4dd7-a769-d0121f02b80e

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics relative to their own
expected application. Another possibility that opens is to better
answer the question ``what is the best general-purpose triple
store?''. I.e. can we collapse all the metrics into a single
\emph{test statistic} that can summarize the performance of the engine
as a whole? Also, can we provide a system to developers that they can
use to see if any changes they do to the engine has unexpected adverse
effects on other parts of the system?

>>>>

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' and those who ask are not
prepared to provide any further qualification. This prompts the
question: Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system to developers that they can use
to see if any changes they do to the engine has unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose?
